Hydra Battles and Cie

### 2021-09-06 doc/part-hydras.tex
try to make Ordering_Functions a type class

\subsubsection{The definition of zero}

@@

\input{movies/snippets/Schutte_basics/iotaDemo}

Indeed, the basic logic of  \coq{} does not allow us to eliminate a proof of a proposition 
$\exists!\,x:A,\,P(x)$ for building a term whose type lies in the sort \texttt{Type}. 
The reasons for this impossibility are explained in many documents~\cite{BC04, chlipalacpdt2011, Coq}.

@@

\begin{Coqsrc}
Axiom epsilon_statement:
  forall (A : Type) (P : A->Prop), inhabited A ->
    {x : A | (exists x, P x) -> P x}.
\end{Coqsrc}

Hilbert's $\epsilon$ \emph{operator} is derived from this  axiom.

\begin{Coqsrc}
Definition epsilon (A : Type) (i:inhabited A) (P : A->Prop) : A
  := proj1_sig (epsilon_statement P i).

Lemma constructive_indefinite_description :
  forall (A : Type) (P : A->Prop),
    (exists x, P x) -> { x : A | P x }.
\end{Coqsrc}

@@

\begin{Coqsrc}
Definition iota (A : Type) (i:inhabited A) (P : A->Prop) : A
  := proj1_sig (iota_statement P i).
\end{Coqsrc}

\begin{Coqsrc}
 Lemma constructive_definite_description :
  forall (A : Type) (P : A->Prop),
    (exists! x, P x) -> { x : A | P x }.
\end{Coqsrc}

\begin{Coqsrc}
Definition iota_spec (A : Type) (i:inhabited A) (P : A->Prop) :
  (exists! x:A, P x) -> P (iota i P)
  := proj2_sig (iota_statement P i).
\end{Coqsrc}

Indeed, the operators \texttt{epsilon} and \texttt{iota} allowed us to make our definitions 
quite close to Schütte's text. Our libraries \href{../theories/html/hydras.Schutte.MoreEpsilonIota.html}%
{\texttt{Schutte.MoreEpsilonIota}}
and
\href{../theories/html/hydras.Schutte.PartialFun.html}%
{\texttt{Schutte.PartialFun}} are extensions of \texttt{Coq.logic.Epsilon} for making easier 
such definitions. See also an article in french~\cite{PCiota}.

@@

\input{movies/snippets/Well_Orders/leastMemberDef}
\input{movies/snippets/Well_Orders/theLeast}

@@

Since we won't be able to prove the proposition
\linebreak \Verb|{exists! a: Ord, least_member (Empty_set Ord) a|, the only properties we would be able to prove about \texttt{bottom} would be \emph{trivial} properties, 
\emph{i.e.}, satisfied by \emph{any} element of type \texttt{Ord}, like for instance
\texttt{bottom = bottom}, or \texttt{zero <= bottom}.

@@

Using \texttt{succ}, it is now easy to define recursively all the finite ordinals.

@@

\input{movies/snippets/Schutte_basics/omegaProps}

@@

>>>>

\subsection{The definition of zero}

@@

\input{movies/snippets/Schutte_basics/iotaDemoa}
\input{movies/snippets/Schutte_basics/iotaDemob}

Indeed, the logic of  \coq{} does not allow us to eliminate a proof of a proposition 
$\exists!\,x:A,\,P(x)$ for building a term whose type lies in the sort \texttt{Type}. 
The reasons for this impossibility are explained in many documents~\cite{BC04, chlipalacpdt2011, Coq}.

@@

\inputsnippets{MoreEpsilonIota/EpsilonStatement}

\emph{Hilbert's $\epsilon$ operator} is derived from this  axiom.

\inputsnippets{MoreEpsilonIota/EpsilonDef}

@@

\inputsnippets{MoreEpsilonIota/IotaDef}

Indeed, the operators \texttt{epsilon} and \texttt{iota} allow us to write formal definitions close to Schütte's text. Our libraries \href{../theories/html/hydras.Schutte.MoreEpsilonIota.html}%
{\texttt{Schutte.MoreEpsilonIota}}
and
\href{../theories/html/hydras.Schutte.PartialFun.html}%
{\texttt{Schutte.PartialFun}} are extensions of \texttt{Coq.logic.Epsilon} for making easier 
such definitions. See also an article in french~\cite{PCiota}.

@@

\input{movies/snippets/Well_Orders/theLeast}

@@

Since we won't be able to prove the proposition
\linebreak \Verb|exists! a: Ord, least_member (Empty_set Ord) a|, the only properties we would be able to prove about \texttt{bottom} would be \emph{trivial} properties, 
\emph{i.e.}, satisfied by \emph{any} element of type \texttt{Ord}, like for instance
\texttt{bottom = bottom}, or \texttt{zero <= bottom}.

@@

Using \texttt{succ}, it is now easy to define recursively the set of the  finite ordinals.

@@

\input{movies/snippets/Schutte_basics/omegaPropsa}
\input{movies/snippets/Schutte_basics/omegaPropsb}
\input{movies/snippets/Schutte_basics/omegaPropsc}
\input{movies/snippets/Schutte_basics/omegaPropsd}

@@

\begin{todo}
Define \texttt{ordering\_function} as a type class !
\end{todo}
